Application of integer linear programming to scheduling clinician on-call service in Toronto hospital: case study

### 2021-01-27 paper/paper.discussion.tex
Work on new 'Practical Considerations' section

In our simulations, we also found that increasing the number of requests per
clinician did not affect the runtime of the algorithm, highlighting the
flexibility of the tool to incorporate clinician preferences. Further, we saw
that the algorithm can accommodate an increase in time-horizon up to four years
with little impact on runtime, suggesting the algorithm can be used generate
schedules far in advance. A key limitation we identified was the sensitivity
of the runtime to larger numbers of services offered by a single department. 
One solution to mitigate the runtime issues created by a
larger number of services would be removing the constraint that prevents
assignment of consecutive blocks, followed by manual readjustment from the
generated schedule.
Overall, our sensitivity analyses using simulated data provided reassurance that
the ILP formulation can be applied to schedule clinicians across real-world
variability between clinical departments.
Next steps include expanding the generalizability of the tool beyond smaller
clinical departments to larger departments within and outside of health-care --
especially those that provide multiple services in parallel for patients and
other clients. As well, additional work can be done to incorporate other
clinician preferences, such as the ability to request time-on slots or preference
for time of year.

>>>>

In our simulations, we also found that increasing the number of requests per
clinician did not affect the runtime of the algorithm, highlighting the
flexibility of the tool to incorporate clinician preferences. Further, we saw
that the algorithm can accommodate an increase in time-horizon up to four years
with little impact on runtime, suggesting the algorithm can be used to generate
schedules far in advance. A key limitation we identified was the sensitivity
of the runtime to larger numbers of services offered by a single department. 
One solution to mitigate the runtime issues created by a
larger number of services would be removing the constraint that prevents
assignment of consecutive blocks, followed by manual readjustment from the
generated schedule.
Overall, our sensitivity analyses using simulated data provided reassurance that
the ILP formulation can be applied to schedule clinicians across real-world
variability between clinical departments.
Next steps include expanding the generalizability of the tool beyond smaller
clinical departments to larger departments within and outside of health-care --
especially those that provide multiple services in parallel for patients and
other clients. As well, additional work can be done to incorporate other
clinician preferences, such as the ability to request time-on slots or preference
for time of year.

### 2021-01-27 paper/paper.tex
Work on comparison/lit review section
Work on comparison section
Add conflict of interest statement
Work on new 'Practical Considerations' section

\documentclass[]{article}
\input{paper.includes.tex}

\title{A flexible integer linear programming formulation for scheduling
	clinician on-call service in hospitals}
\date{}

@@

	\section{Introduction}\label{sec:introduction}
	\input{paper.intro.tex}
	\section{Problem}\label{sec:problem}
	\input{paper.problem.tex}
	\section{Methods}\label{sec:methods}
	\input{paper.methods.tex}
	\section{Experiments}\label{sec:experiments}
	\input{paper.experiments.tex}
	\section{Discussion}\label{sec:discussion}
	\input{paper.discussion.tex}
	\section{Acknowledgements}\label{sec:acknowledgements}
	\input{paper.acknowledgements.tex}
	\section{Funding}\label{sec:funding}
	\input{paper.funding.tex}

	\bibliographystyle{unsrt}
	\bibliography{references}
\end{document}

>>>>

\documentclass[]{article}
\input{paper.includes.tex}
\addbibresource{references.bib}

%\title{A flexible integer linear programming formulation for scheduling
%	clinician on-call service in hospitals}
\title{
	Application of integer linear programming to scheduling clinician
	on-call service in Toronto hospital: case study
}
\date{}

@@

	\section{Introduction}\label{sec:introduction}
	\input{paper.intro.tex}
	\section{Problem Description}\label{sec:problem}
	\input{paper.problem.tex}
	\section{Mathematical Formulation}\label{sec:methods}
	\input{paper.methods.tex}
	\section{Categorization and Comparison with Other Models}\label{sec:comparison}
	\input{paper.comparison.tex}
	\section{Computational Experiments}\label{sec:experiments}
	\input{paper.experiments.tex}
	\section{Practical Considerations}\label{sec:practical}
	\input{paper.practical.tex}
	\section{Discussion}\label{sec:discussion}
	\input{paper.discussion.tex}
	\section{Acknowledgements}\label{sec:acknowledgements}
	\input{paper.acknowledgements.tex}
	\section{Funding}\label{sec:funding}
	\input{paper.funding.tex}
	\section{Conflict of Interest}
	On behalf of all authors, the corresponding author states that there is no conflict of interest.

	\printbibliography
\end{document}
